Lossy compression of DNA sequencing quality data

### 2015-05-07 manuscript/q-compression.tex
trivial edits

\title[lossy-compression]{Lossy compression of DNA sequencing quality
  data} \author[Hill \textit{et~al.}]{Christopher
  M. Hill\,$^{1}$, Andr\'{a}s Szolek\,$^{2}$, Mohamed El
  Hadidi\,$^{3}$, and Michael P. Cummings\,$^4$\footnote{to whom correspondence should be
    addressed}} \address{$^{1}$Department of Computer Science, University of Maryland,
  College Park, Maryland, 20742 USA\\ $^{2}$Department of Applied
  Bioinformatics, Center for Bioinformatics, Quantitative Biology
  Center, and Department of Computer Science, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany\\ 
  $^{3}$Department of Algorithms in
  Bioinformatics, Center for Bioinformatics, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany
  \\ $^{4}$ Center for Bioinformatics and Computational Biology, University of
  Maryland, College Park, Maryland, 20742 USA}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXX}
\editor{Associate Editor: XXXXXXX}

@@

Profiles can be obtained from techniques other than $k$-means clustering.
%While we focus on profiles obtained from $k$-means clustering, other profiling techniques can be used in practice.
We can store the profiles of polynomial functions to increase the compressibility of polynomial regression modeling.
%For example, in order to increase the compressibility of polynomial regression modeling, we can store the profiles of polynomial functions.
In other words, we can use a spline (a function that is piecewise-defined by polynomial functions) to represent a given quality sequence.
Exploring other potential applications of profile-based compression is outside the scope of this work.

>>>>

\title[lossy-compression]{Lossy compression of DNA sequencing quality
  data}

\author[Hill \textit{et~al.}]{Christopher M. Hill\,$^{1}$, Andr\'{a}s
  Szolek\,$^{2}$, Mohamed El Hadidi\,$^{3}$, and Michael
  P. Cummings\,$^4$\footnote{to whom correspondence should be
    addressed}} \address{$^{1}$Department of Computer Science,
  University of Maryland, College Park, Maryland, 20742
  USA\\ $^{2}$Department of Applied Bioinformatics, Center for
  Bioinformatics, Quantitative Biology Center, and Department of
  Computer Science, University of T\"{u}bingen, Sand 14, 72076
  T\"{u}bingen, Germany\\ $^{3}$Department of Algorithms in
  Bioinformatics, Center for Bioinformatics, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany \\ $^{4}$ Center
  for Bioinformatics and Computational Biology, University of
  Maryland, College Park, Maryland, 20742 USA}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXX}

\editor{Associate Editor: XXXXXXX}

@@

Profiles can be obtained from techniques other than $k$-means
clustering. We can store the profiles of polynomial functions to
increase the compressibility of polynomial regression modeling.  In
other words, we can use a spline (a function that is piecewise-defined
by polynomial functions) to represent a given quality sequence.
However, we have not explored any of these other approaches here.
